### 2021-09-12 preprint.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@10d3ec7b9a0f1971639bbb23d35465392c675424 🚀
Deploying to gh-pages from @ PoisotLab/manuscript-template@5062ccb647f4ebdddcbda9a464ecccad739503d5 🚀

\geometry{includemp,
            letterpaper,
            top=1.0in,
            bottom=2.510cm,
            inner=0.5in,
            outer=0.4in,
            marginparwidth=2.1in,
            marginparsep=0.3in}

\usepackage[singlelinecheck=off]{caption}
\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}
\usepackage{floatrow}
\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}
\floatsetup[table]{margins=hangoutside,
             facing=yes,
             capposition=beside,
             capbesideposition={center,outside},
             floatwidth=\textwidth}

>>>>

\geometry{includemp,
            letterpaper,
            top=1.0in,
            bottom=2.510cm,
            left=0.35in,
            right=0.35in,
            marginparwidth=2.0in,
            marginparsep=0.35in}

\usepackage[singlelinecheck=off]{caption}
\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}
\usepackage{floatrow}
\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}
\floatsetup[table]{margins=hangright,
             facing=no,
             capposition=beside,
             capbesideposition={center,outside},
             floatwidth=\textwidth}
